---
title: "Out-of-Model Feature Figures"
author: "Grace Jacobs"
output: html_document
---


```{r setup, include=FALSE}
library(haven)
library(ggplot2)
library(ggpubr)
library(plotrix)
library(tidyverse)
library(reshape2)

source("code/2_Comparing_subgroups/setting_up_data_for_cluster_analysis.r")

# loading density summaries for data-driven and diagnostic groups across strength thresholds
density <- read.csv("../../output/4_Out-of-model_features/Structural_Covariance/group_density_adjusted.csv", header=TRUE)
density <- melt(density, id.vars = "Threshold", measure.vars = c("G1", "G2", "G3", "G4"))

density_clin <- read.csv("../../output/4_Out-of-model_features/Structural_Covariance/clin_density_adjusted.csv", header=TRUE, sep=",")
density_clin <- density_clin[-c(24) ,] #removing the average row
density_clin$Threshold <- as.numeric(density_clin$Threshold)
density_clin <- melt(density_clin, id.vars = "Threshold", measure.vars = c("adhd", "asd", "ocd"))

```


### Adaptive behavior Assessment System - general adaptive composite  
 
Data-driven Groups  

```{r, echo=FALSE}
all$AB21GCCS_resid <- resid(lm(AB21GCCS~GENDER + age + IQ, data=all, na.action=na.exclude))
my_comparisons <- list( c("1", "2"), c("1", "3"), c("1", "4"))

ggplot(all, aes(x=group, y=AB21GCCS_resid, colour = group)) +
  geom_boxplot() +
    theme_classic() +
  geom_point(aes(fill = clin_diagnosis), size = 2, colour = "black", shape = 21, position = position_jitterdodge()) +
    scale_fill_manual(values=c("black", "darkgray", "white")) +
    scale_color_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "mediumpurple")) +
  ggtitle("Adaptive Functioning Score") +
  labs(y= "Total Score", x="Group", legend.title = " Clinical Diagnosis") +
    theme(axis.text.y=element_text(size=18), axis.text.x=element_text(size=18), 
  axis.title.y=element_text(size=18),axis.title.x=element_text(size=18), legend.text=element_text(size=18),plot.title = element_text(size=20), legend.title=element_blank()) +
  stat_compare_means(label = "p.signif", comparisons = my_comparisons, method = "t.test", p.adjust.method = "fdr") +
  scale_y_continuous(limits=c(-40, 80), breaks =c(-20, 0, 20, 40, 60, 80))

ggsave("../../output/4_Out-of-model_features/Figures/genadaptfunc_resid_groups.png", plot = last_plot(), width = 7, height = 5)

```

Diagnostic Groups  

```{r, echo=FALSE}
my_comparisons <- list( c("ASD", "OCD"), c("ASD", "ADHD"))
all$AB21GCCS_resid <- resid(lm(AB21GCCS~GENDER + age + IQ, data=all, na.action=na.exclude))

ggplot(all, aes(x=clin_diagnosis, y=AB21GCCS_resid)) +
  geom_boxplot() +
    theme_classic() +
  geom_point(aes(fill = group), size = 2, colour = "black", shape = 21, position = position_jitterdodge()) +
    scale_color_manual(values=c("black", "darkgray", "white")) +
    scale_fill_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "mediumpurple")) +
  ggtitle("Adaptive Functioning Score") +
  labs(y= "Total Score", x="Group", legend.title = " Clinical Diagnosis") +
    theme(axis.text.y=element_text(size=18), axis.text.x=element_text(size=18), 
  axis.title.y=element_text(size=18),axis.title.x=element_blank(), legend.text=element_text(size=18),plot.title = element_text(size=20), legend.title=element_blank()) +
  stat_compare_means(label = "p.signif", comparisons = my_comparisons, method = "t.test", p.adjust.method = "fdr") +
  scale_y_continuous(limits=c(-40, 80), breaks =c(-20, 0, 20, 40, 60, 80))
  
ggsave("../../output/4_Out-of-model_features/Figures/genadaptfunc_resid_dx.png", plot = last_plot(), width = 7, height = 5)

```


## Surface Area Plots - the left insula is the only significant area when the top 10 CT regions are analysed  

Data-driven Groups  

```{r, echo=FALSE}
all$L_insula_surfavg_resid <- resid(lm(L_insula_surfavg~GENDER + IQ + age, data=all, na.action = na.exclude))
my_comparisons <- list( c("4", "2"))

ggplot(all, aes(x=group, y=L_insula_surfavg_resid, color=group)) +
  geom_boxplot() +
    theme_classic() +
  ggtitle("Left Insula Surface Area") +
  geom_point(aes(fill = clin_diagnosis, color = group), size = 2, colour= "black", shape = 21, position = position_jitterdodge()) +
    scale_fill_manual(values=c("black", "darkgray", "white")) +
  scale_color_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "mediumpurple")) +
  labs(y= "Surface Area (mm )", x="Group", legend.title = " Clinical Diagnosis") +
    theme(axis.text.y=element_text(size=18), axis.text.x=element_text(size=18), 
  axis.title.y=element_text(size=18),axis.title.x=element_text(size=18), legend.text=element_text(size=18),plot.title = element_text(size=22), legend.title=element_blank(), text=(element_text(family="Arial")))  +
  stat_compare_means(comparisons = my_comparisons, method = "t.test", label = "p.signif", p.adjust.method = "fdr") +
    scale_y_continuous(limits=c(-500, 1000), breaks =c(-500, 0, 500, 1000))


ggsave("../../output/4_Out-of-model_features/Figures/L_insula_surfavg_groups.png", plot = last_plot())

```


Diagnostic groups  

```{r, echo=FALSE}
all$L_insula_surfavg_resid <- resid(lm(L_insula_surfavg~GENDER + IQ + age, data=all, na.action = na.exclude))
my_comparisons <- list( c("ASD", "OCD"))

ggplot(all, aes(x=clin_diagnosis, y=L_insula_surfavg_resid)) +
  geom_boxplot() +
    theme_classic() +
  ggtitle("Left Insula Surface Area") +
  geom_point(aes(fill = group, color = group), size = 2, colour= "black", shape = 21, position = position_jitterdodge()) +
    scale_color_manual(values=c("black", "darkgray", "white")) +
    scale_fill_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "mediumpurple")) +
  labs(y= "Surface Area (mm )", x="Group", legend.title = " Clinical Diagnosis") +
    theme(axis.text.y=element_text(size=18), axis.text.x=element_text(size=18), 
  axis.title.y=element_text(size=18),axis.title.x=element_text(size=18), legend.text=element_text(size=18),plot.title = element_text(size=22), legend.title=element_blank(), text=(element_text(family="Arial"))) +
  scale_y_continuous(limits=c(-500, 1000), breaks =c(-500, 0, 500, 1000))


ggsave("../../output/4_Out-of-model_features/Figures/L_insula_surfavg_dx.png", plot = last_plot())
```




## Structural Covariance Network Densities across thresholds for data-driven and diagnostic groups    

Data-driven Groups  

```{r, echo=FALSE}
ggplot(density, aes(x=Threshold, y=value, color=variable)) +
  geom_point(size=3) +
  theme_classic() +
  ggtitle("Network Density Across Thresholds") +
      scale_color_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "slateblue")) +
  theme(axis.text.y=element_text(size=20), axis.text.x=element_text(size=20), 
  axis.title.y=element_text(size=22),axis.title.x=element_text(size=22),plot.title = element_text(size=24), legend.title = element_blank(), legend.text =element_blank()) +
  labs(y= "Density", x="Threshold (Pearson r)") +
  scale_y_continuous(limits=c(0, 0.8), breaks =c(0.2, 0.4, 0.6, 0.8))
  #geom_smooth(alpha=0.2, method=lm) 
  
ggsave("../../output/4_Out-of-model_features/Figures/density_across_thresholds_groups.png", plot = last_plot())

```

Diagnostic Groups  

```{r, echo=FALSE}
ggplot(density_clin, aes(x=Threshold, y=value, color=variable)) +
  geom_point(size=3, aes(color = variable, fill=variable), colour= "black", shape = 21) +
  theme_classic() +
  ggtitle("Network Density Across Thresholds") +
      scale_color_manual(values=c("black", "darkgray", "white")) +
        scale_fill_manual(values=c("black", "darkgray", "white")) +
  theme(axis.text.y=element_text(size=20), axis.text.x=element_text(size=20), 
  axis.title.y=element_text(size=22),axis.title.x=element_text(size=22),plot.title = element_text(size=24), legend.title = element_blank(), legend.text =element_blank()) +
  labs(y= "Density", x="Threshold (Pearson r)") +
  scale_y_continuous(limits=c(0, 0.8), breaks =c(0.2, 0.4, 0.6, 0.8))
  #geom_smooth(alpha=0.2, method=lm) 
  
ggsave("../../output/4_Out-of-model_features/Figures/density_across_thresholds_dx.png", plot = last_plot())

```



