---
title: "Random Forest Model figures"
author: "Grace Jacobs"

---

```{r setup, include=FALSE}
library(ggplot2)
library(knitr)
library(dplyr)
library(tidyr)
```

```{r, echo=FALSE}
new <- read.csv("../../output/1_SNF_analysis/4clust_groups_k18_0.8_1000perms.csv")
new$groups_2 <- ifelse(new$groups == "1", "2", NA)
new$groups_2 <- ifelse(new$groups == "2", "4", new$groups_2)
new$groups_2 <- ifelse(new$groups == "3", "3", new$groups_2)
new$groups_2 <- ifelse(new$groups == "4", "1", new$groups_2)
new$groups <- new$groups_2

directory <- ("../../output/5_Supervised_classification")

```

## Random Forest model

###All features by NMI

```{r, echo=FALSE}
model <- "all_mtry80"

options(scipen=999)
adjrandindex <- read.csv(file=file.path(directory, paste("list_adjrandidx_100perms_", model, ".csv", sep="")))
adjrandindex$X <- 1
adjrandindex$X <- as.factor(adjrandindex$X)
names(adjrandindex) <- c("X", "index")

acc_by_group <- read.csv(file=file.path(directory, paste("acc_by_group_100perms_", model, ".csv", sep="")))
acc_by_group <- acc_by_group[-c(1), ]
acc_by_group$label <- rep(1:4, times=100, each=1)
acc_by_group$label <- as.factor(acc_by_group$label)

acc_overall <- read.csv(file=file.path(directory, paste("acc_overall_100perms_", model, ".csv", sep="")))
acc_overall <- as.data.frame(t(acc_overall))
names <- acc_overall[1,]
colnames(acc_overall) <- t(names)
acc_overall <- acc_overall[-1,]
acc_overall$X <- 1
acc_overall$X <- as.factor(acc_overall$X)
acc_overall$Accuracy <- as.numeric(as.character(acc_overall$Accuracy))

mean(acc_overall$Accuracy)

filter(acc_by_group) %>%
  group_by(label) %>%
  summarise(Sensitivity=mean(byClass.Sensitivity))
filter(acc_by_group) %>%
  group_by(label) %>%
  summarise(Spec=mean(byClass.Specificity))
```

#### All features by NMI - Plotting Adjusted Rand Index

```{r, echo=FALSE}
ggplot(adjrandindex, aes(x=X, y=index)) +
  geom_boxplot() +
  theme_classic() +
   labs(y= "Adjusted Rand Index") +
  geom_point(aes(fill = index), size = 2.5, shape = 21, position = position_jitterdodge()) +
   theme(axis.text.y=element_text(size=25), axis.text.x=element_blank(),
  axis.title.y=element_text(size=25),axis.title.x=element_blank(), legend.position = "none") +
  stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = .75, linetype = "dashed")+
  scale_y_continuous(limits=c(0, 1), breaks =c(0, 0.2, 0.4, 0.6, 0.8, 1))

ggsave(file=file.path(directory, paste("Figures/All_features_ARI.png", sep="")), plot = last_plot(), , width = 3, height = 4)
```

#### All features by NMI - Plotting overall accuracy

```{r, echo=FALSE}
mean(acc_overall$Accuracy)

ggplot(acc_overall, aes(x=X, y=Accuracy)) +
  geom_boxplot() +
  theme_classic() +
   labs(y= "Overall Accuracy") +
  geom_point(aes(fill = Accuracy), size = 2.5, shape = 21, position = position_jitterdodge()) +
   theme(axis.text.y=element_text(size=25), axis.text.x=element_blank(),
  axis.title.y=element_text(size=25),axis.title.x=element_blank(), legend.position = "none") +
  stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = .75, linetype = "dashed") +
  scale_y_continuous(limits=c(0, 1), breaks =c(0, 0.2, 0.4, 0.6, 0.8, 1))

ggsave(file=file.path(directory, paste("Figures/All_features_accuracy.png", sep="")), plot = last_plot(), , width = 3, height = 4)

```

#### All features by NMI - Plotting sensitivity by group

```{r, echo=FALSE}
ggplot(acc_by_group, aes(x=label, y=byClass.Sensitivity)) +
  geom_boxplot() +
  theme_classic() +
   labs(y= "Sensitivity", x="Group", legend.title = " Clinical Diagnosis") +
  geom_point(aes(fill = label), size = 2.5, shape = 21, position = position_jitterdodge()) +
  scale_fill_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "mediumpurple")) +
   theme(axis.text.y=element_text(size=25), axis.text.x=element_text(size=25),
  axis.title.y=element_text(size=25),axis.title.x=element_blank(), legend.position = "none") +
  stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = .75, linetype = "dashed") +
  scale_y_continuous(limits=c(0, 1), breaks =c(0, 0.2, 0.4, 0.6, 0.8, 1))

test <- acc_by_group[which(acc_by_group$label == "2"), ]
mean(test$byClass.Sensitivity)

ggsave(file=file.path(directory, paste("Figures/All_features_sensitivity.png", sep="")), plot = last_plot(), width = 6, height = 4)
```

#### All features by NMI - Plotting specificity by group

```{r, echo=FALSE}
ggplot(acc_by_group, aes(x=label, y=byClass.Specificity)) +
  geom_boxplot() +
   labs(y= "Specificity", x="Group", legend.title = " Clinical Diagnosis") +
  geom_point(aes(fill = label), size = 2.5, shape = 21, position = position_jitterdodge()) +
  theme_classic() +
  scale_fill_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "mediumpurple")) +
   theme(axis.text.y=element_text(size=25), axis.text.x=element_text(size=25),
  axis.title.y=element_text(size=25),axis.title.x=element_blank(), legend.position = "none") +
  stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = .75, linetype = "dashed") +
  scale_y_continuous(limits=c(0, 1), breaks =c(0, 0.2, 0.4, 0.6, 0.8, 1))


ggsave(file=file.path(directory, paste("Figures/All_features_specificity.png", sep="")), plot = last_plot(), , width = 6, height = 4)
```

******

###Top 10 features by NMI
```{r, echo=FALSE}
model <- "top10_mtry5"

options(scipen=999)
adjrandindex <- read.csv(file=file.path(directory, paste("list_adjrandidx_100perms_", model, ".csv", sep="")))
adjrandindex$X <- 1
adjrandindex$X <- as.factor(adjrandindex$X)
names(adjrandindex) <- c("X", "index")

acc_by_group <- read.csv(file=file.path(directory, paste("acc_by_group_100perms_", model, ".csv", sep="")))
acc_by_group <- acc_by_group[-c(1), ]
acc_by_group$label <- rep(1:4, times=100, each=1)
acc_by_group$label <- as.factor(acc_by_group$label)

acc_overall <- read.csv(file=file.path(directory, paste("acc_overall_100perms_", model, ".csv", sep="")))
acc_overall <- as.data.frame(t(acc_overall))
names <- acc_overall[1,]
colnames(acc_overall) <- t(names)
acc_overall <- acc_overall[-1,]
acc_overall$X <- 1
acc_overall$X <- as.factor(acc_overall$X)
acc_overall$Accuracy <- as.numeric(as.character(acc_overall$Accuracy))

mean(acc_overall$Accuracy)

filter(acc_by_group) %>%
  group_by(label) %>%
  summarise(Sensitivity=mean(byClass.Sensitivity))
filter(acc_by_group) %>%
  group_by(label) %>%
  summarise(Spec=mean(byClass.Specificity))
```

#### Top 10 by NMI - Plotting Adjusted Rand Index

```{r, echo=FALSE}
ggplot(adjrandindex, aes(x=X, y=index)) +
  geom_boxplot() +
  theme_classic() +
   labs(y= "Adjusted Rand Index") +
  geom_point(aes(fill = index), size = 2.5, shape = 21, position = position_jitterdodge()) +
   theme(axis.text.y=element_text(size=25), axis.text.x=element_blank(),
  axis.title.y=element_text(size=25),axis.title.x=element_blank(), legend.position = "none") +
  stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = .75, linetype = "dashed")+
  scale_y_continuous(limits=c(0, 1), breaks =c(0, 0.2, 0.4, 0.6, 0.8, 1))

ggsave(file=file.path(directory, paste("Figures/10_features_ARI.png", sep="")), plot = last_plot(), , width = 3, height = 4)
```

#### Top 10 by NMI - Plotting overall accuracy

```{r, echo=FALSE}
mean(acc_overall$Accuracy)

ggplot(acc_overall, aes(x=X, y=Accuracy)) +
  geom_boxplot() +
  theme_classic() +
   labs(y= "Overall Accuracy") +
  geom_point(aes(fill = Accuracy), size = 2.5, shape = 21, position = position_jitterdodge()) +
   theme(axis.text.y=element_text(size=25), axis.text.x=element_blank(),
  axis.title.y=element_text(size=25),axis.title.x=element_blank(), legend.position = "none") +
  stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = .75, linetype = "dashed") +
  scale_y_continuous(limits=c(0, 1), breaks =c(0, 0.2, 0.4, 0.6, 0.8, 1))

ggsave(file=file.path(directory, paste("Figures/10_features_accuracy.png", sep="")), plot = last_plot(), width = 3, height = 4)

```

#### Top 10 by NMI - Plotting sensitivity by group

```{r, echo=FALSE}
ggplot(acc_by_group, aes(x=label, y=byClass.Sensitivity)) +
  geom_boxplot() +
  theme_classic() +
   labs(y= "Sensitivity", x="Group", legend.title = " Clinical Diagnosis") +
  geom_point(aes(fill = label), size = 2.5, shape = 21, position = position_jitterdodge()) +
  scale_fill_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "mediumpurple")) +
   theme(axis.text.y=element_text(size=25), axis.text.x=element_text(size=25),
  axis.title.y=element_text(size=25),axis.title.x=element_blank(), legend.position = "none") +
  stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = .75, linetype = "dashed") +
  scale_y_continuous(limits=c(0, 1), breaks =c(0, 0.2, 0.4, 0.6, 0.8, 1))

test <- acc_by_group[which(acc_by_group$label == "2"), ]
mean(test$byClass.Sensitivity)

ggsave(file=file.path(directory, paste("Figures/10_features_sensitivity.png", sep="")), plot = last_plot(), width = 6, height = 4)

```

#### Top 10 features by NMI - Plotting specificity by group

```{r, echo=FALSE}
ggplot(acc_by_group, aes(x=label, y=byClass.Specificity)) +
  geom_boxplot() +
   labs(y= "Specificity", x="Group", legend.title = " Clinical Diagnosis") +
  geom_point(aes(fill = label), size = 2.5, shape = 21, position = position_jitterdodge()) +
  theme_classic() +
  scale_fill_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "mediumpurple")) +
   theme(axis.text.y=element_text(size=25), axis.text.x=element_text(size=25),
  axis.title.y=element_text(size=25),axis.title.x=element_blank(), legend.position = "none") +
  stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = .75, linetype = "dashed") +
  scale_y_continuous(limits=c(0, 1), breaks =c(0, 0.2, 0.4, 0.6, 0.8, 1))


ggsave(file=file.path(directory, paste("Figures/10_features_specificity.png", sep="")), plot = last_plot(), width = 6, height = 4)
```

*****

###Top 35 by NMI
```{r, echo=FALSE}
model <- "top35_mtry15"

options(scipen=999)
adjrandindex <- read.csv(file=file.path(directory, paste("list_adjrandidx_100perms_", model, ".csv", sep="")))
adjrandindex$X <- 1
adjrandindex$X <- as.factor(adjrandindex$X)
names(adjrandindex) <- c("X", "index")

acc_by_group <- read.csv(file=file.path(directory, paste("acc_by_group_100perms_", model, ".csv", sep="")))
acc_by_group <- acc_by_group[-c(1), ]
acc_by_group$label <- rep(1:4, times=100, each=1)
acc_by_group$label <- as.factor(acc_by_group$label)

acc_overall <- read.csv(file=file.path(directory, paste("acc_overall_100perms_", model, ".csv", sep="")))
acc_overall <- as.data.frame(t(acc_overall))
names <- acc_overall[1,]
colnames(acc_overall) <- t(names)
acc_overall <- acc_overall[-1,]
acc_overall$X <- 1
acc_overall$X <- as.factor(acc_overall$X)
acc_overall$Accuracy <- as.numeric(as.character(acc_overall$Accuracy))

mean(acc_overall$Accuracy)

filter(acc_by_group) %>%
  group_by(label) %>%
  summarise(Sensitivity=mean(byClass.Sensitivity))
filter(acc_by_group) %>%
  group_by(label) %>%
  summarise(Spec=mean(byClass.Specificity))
```

#### Top 35 by NMI - Plotting Adjusted Rand Index

```{r, echo=FALSE}
ggplot(adjrandindex, aes(x=X, y=index)) +
  geom_boxplot() +
  theme_classic() +
   labs(y= "Adjusted Rand Index") +
  geom_point(aes(fill = index), size = 2.5, shape = 21, position = position_jitterdodge()) +
   theme(axis.text.y=element_text(size=25), axis.text.x=element_blank(),
  axis.title.y=element_text(size=25),axis.title.x=element_blank(), legend.position = "none") +
  stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = .75, linetype = "dashed")+
  scale_y_continuous(limits=c(0, 1), breaks =c(0, 0.2, 0.4, 0.6, 0.8, 1))

ggsave(file=file.path(directory, paste("Figures/35_features_ARI.png", sep="")), plot = last_plot(), width = 3, height = 4)
```

#### Top 35 by NMI - Plotting overall accuracy

```{r, echo=FALSE}
mean(acc_overall$Accuracy)

ggplot(acc_overall, aes(x=X, y=Accuracy)) +
  geom_boxplot() +
  theme_classic() +
   labs(y= "Overall Accuracy") +
  geom_point(aes(fill = Accuracy), size = 2.5, shape = 21, position = position_jitterdodge()) +
   theme(axis.text.y=element_text(size=25), axis.text.x=element_blank(),
  axis.title.y=element_text(size=25),axis.title.x=element_blank(), legend.position = "none") +
  stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = .75, linetype = "dashed") +
  scale_y_continuous(limits=c(0, 1), breaks =c(0, 0.2, 0.4, 0.6, 0.8, 1))

ggsave(file=file.path(directory, paste("Figures/35_features_accuracy.png", sep="")), plot = last_plot(), width = 3, height = 4)

```

#### Top 35 by NMI - Plotting sensitivity by group

```{r, echo=FALSE}
ggplot(acc_by_group, aes(x=label, y=byClass.Sensitivity)) +
  geom_boxplot() +
  theme_classic() +
   labs(y= "Sensitivity", x="Group", legend.title = " Clinical Diagnosis") +
  geom_point(aes(fill = label), size = 2.5, shape = 21, position = position_jitterdodge()) +
  scale_fill_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "mediumpurple")) +
   theme(axis.text.y=element_text(size=25), axis.text.x=element_text(size=25),
  axis.title.y=element_text(size=25),axis.title.x=element_blank(), legend.position = "none") +
  stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = .75, linetype = "dashed") +
  scale_y_continuous(limits=c(0, 1), breaks =c(0, 0.2, 0.4, 0.6, 0.8, 1))

test <- acc_by_group[which(acc_by_group$label == "2"), ]
mean(test$byClass.Sensitivity)

ggsave(file=file.path(directory, paste("Figures/35_features_sensitivity.png", sep="")), plot = last_plot(), width = 6, height = 4)
```

#### Top 35 features by NMI - Plotting specificity by group

```{r, echo=FALSE}
ggplot(acc_by_group, aes(x=label, y=byClass.Specificity)) +
  geom_boxplot() +
   labs(y= "Specificity", x="Group", legend.title = " Clinical Diagnosis") +
  geom_point(aes(fill = label), size = 2.5, shape = 21, position = position_jitterdodge()) +
  theme_classic() +
  scale_fill_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "mediumpurple")) +
   theme(axis.text.y=element_text(size=25), axis.text.x=element_text(size=25),
  axis.title.y=element_text(size=25),axis.title.x=element_blank(), legend.position = "none") +
  stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = .75, linetype = "dashed") +
  scale_y_continuous(limits=c(0, 1), breaks =c(0, 0.2, 0.4, 0.6, 0.8, 1))

ggsave(file=file.path(directory, paste("Figures/35_features_specificity.png", sep="")), plot = last_plot(), width = 6, height = 4)

```


***
###Top 2 features from each data type
```{r, echo=FALSE}
model <- "top2_mtry4"

adjrandindex <- read.csv(file=file.path(directory, paste("list_adjrandidx_100perms_", model, ".csv", sep="")))
adjrandindex$X <- 1
adjrandindex$X <- as.factor(adjrandindex$X)
names(adjrandindex) <- c("X", "index")

acc_by_group <- read.csv(file=file.path(directory, paste("acc_by_group_100perms_", model, ".csv", sep="")))
acc_by_group <- acc_by_group[-c(1), ]
acc_by_group$label <- rep(1:4, times=100, each=1)
acc_by_group$label <- as.factor(acc_by_group$label)
acc_overall <- read.csv(file=file.path(directory, paste("acc_overall_100perms_", model, ".csv", sep="")))
acc_overall <- as.data.frame(t(acc_overall))
names <- acc_overall[1,]
colnames(acc_overall) <- t(names)
acc_overall <- acc_overall[-1,]
acc_overall$X <- 1
acc_overall$X <- as.factor(acc_overall$X)
acc_overall$Accuracy <- as.numeric(as.character(acc_overall$Accuracy))

mean(acc_overall$Accuracy)
acc_by_group$X <- seq(1, 4, 1)
test <- acc_by_group[which(acc_by_group$X == "3"), ]
mean(test$byClass.Balanced.Accuracy)

mean(acc_overall$Accuracy)

filter(acc_by_group) %>%
  group_by(label) %>%
  summarise(Sensitivity=mean(byClass.Sensitivity))
filter(acc_by_group) %>%
  group_by(label) %>%
  summarise(Spec=mean(byClass.Specificity))
```


#### Top 2 features by NMI for each of the 4 data types - Plotting Adjusted Rand Index

```{r, echo=FALSE}
ggplot(adjrandindex, aes(x=X, y=index)) +
  geom_boxplot() +
   labs(y= "Adjusted Rand Index") +
  theme_classic() +
  geom_point(aes(fill = index), size = 2.5, shape = 21, position = position_jitterdodge()) +
   theme(axis.text.y=element_text(size=25), axis.text.x=element_blank(),
  axis.title.y=element_text(size=25),axis.title.x=element_blank(), legend.position = "none") +
  stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = .75, linetype = "dashed")+
  scale_y_continuous(limits=c(0, 1), breaks =c(0, 0.2, 0.4, 0.6, 0.8, 1))

ggsave(file=file.path(directory, paste("Figures/top2_features_ARI.png", sep="")), plot = last_plot(), width = 3, height = 4)
```

#### Top 2 features by NMI for each of the 4 data types - Plotting overall accuracy

```{r, echo=FALSE}
ggplot(acc_overall, aes(x=X, y=Accuracy)) +
  geom_boxplot() +
   labs(y= "Overall Accuracy") +
  theme_classic() +
  geom_point(aes(fill = Accuracy), size = 2.5, shape = 21, position = position_jitterdodge()) +
   theme(axis.text.y=element_text(size=25), axis.text.x=element_blank(),
  axis.title.y=element_text(size=25),axis.title.x=element_blank(), legend.position = "none") +
  stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = .75, linetype = "dashed") +
  scale_y_continuous(limits=c(0, 1), breaks =c(0, 0.2, 0.4, 0.6, 0.8, 1))

ggsave(file=file.path(directory, paste("Figures/top2_features_accuracy.png", sep="")), plot = last_plot(), width = 3, height = 4)
```

#### Top 2 features by NMI for each of the 4 data types - Plotting sensitivity by group

```{r, echo=FALSE}
ggplot(acc_by_group, aes(x=label, y=byClass.Sensitivity)) +
  geom_boxplot() +
  theme_classic() +
   labs(y= "Sensitivity", x="Group", legend.title = " Clinical Diagnosis") +
  geom_point(aes(fill = label), size = 2.5, shape = 21, position = position_jitterdodge()) +
  scale_fill_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "mediumpurple")) +
   theme(axis.text.y=element_text(size=25), axis.text.x=element_text(size=25),
  axis.title.y=element_text(size=25),axis.title.x=element_blank(), legend.position = "none") +
  stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = .75, linetype = "dashed") +
  scale_y_continuous(limits=c(0, 1), breaks =c(0, 0.2, 0.4, 0.6, 0.8, 1))

ggsave(file=file.path(directory, paste("Figures/top2_features_sensitivity.png", sep="")), plot = last_plot(), width = 6, height = 4)
```

#### Top 2 features by NMI for each of the 4 data types - Plotting specificity by group

```{r, echo=FALSE}
ggplot(acc_by_group, aes(x=label, y=byClass.Specificity)) +
  geom_boxplot() +
   labs(y= "Specificity", x="Group", legend.title = " Clinical Diagnosis") +
  geom_point(aes(fill = label), size = 2.5, shape = 21, position = position_jitterdodge()) +
  theme_classic() +
  scale_fill_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "mediumpurple")) +
   theme(axis.text.y=element_text(size=25), axis.text.x=element_text(size=25),
  axis.title.y=element_text(size=25),axis.title.x=element_blank(), legend.position = "none") +
  stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = .75, linetype = "dashed") +
  scale_y_continuous(limits=c(0, 1), breaks =c(0, 0.2, 0.4, 0.6, 0.8, 1))


ggsave(file=file.path(directory, paste("Figures/top2_features_specificity.png", sep="")), plot = last_plot(), width = 6, height = 4)
```



