---
title: "POND SNF Cluster comparison analysis"
author: "Grace Jacobs"
output: html_document
---

```{r setup, include=FALSE}
library(effsize)
library(ggplot2)
library(dplyr)
library(tidyr)
library(broom)
library(data.table)
library(ggsignif)
library(dunn.test)
library(tidyr)
library(knitr)
library(png)
library(reshape2)
library(haven)
library(ggpubr)
library(lsr)
library(car)
library(sjstats)
library(agricolae)


#source("code/2_Comparing_subgroups/setting_up_data_for_cluster_analysis.r")

intel <- all[, c("ID", "IQ")]
CT_stacked <- merge(intel, CT_stacked, by="ID")
SA_stacked <- merge(intel, SA_stacked, by="ID")
top_measures <- merge(intel, top_measures, by="ID")
all_features <- merge(intel, all_features, by="ID")
top_10 <- merge(intel, top_10, by="ID")

NMI <- read.csv("../../output/1_SNF_analysis/all_scores_k18_0.8_1000perms.csv")
NMI$Measure <- gsub('-', '.', NMI$Measure)
NMI$Measure <- gsub('/', '.', NMI$Measure)

```


## Cluster analysis - n=176, between the ages of 6-16

###Measures included:  
Cortical thickness from freesurfer  
Subcortical volumes from freesurfer
FA of 46 white matter tracts determined using TBSS 
7 clinical scores from 5 scales   

Parameters below chosen based on SNF guidelines and increasing the NMI scores each data type has with the fused similarity network   
K=18
iterations=10  
hyperparameter=0.8  
No individuals cluster unreliably 

### Similarity Network Fusion Clusters

##Demographics of groups and their symptom severity for clinical symptoms

```{r, echo=FALSE}
Demographics <- filter(all) %>%
  group_by(group) %>%
  summarise(N=length(group), Age=mean(age), Age_sd=sd(age), IQ=mean(IQ, na.rm=TRUE), Internalizing=mean(CB68IPTS, na.rm=TRUE),Internalizing_sd=sd(CB68IPTS, na.rm=TRUE), Externalizing=mean(CB68EPTS, na.rm=TRUE), Externalizing_sd=sd(CB68EPTS, na.rm=TRUE), OC_symps=mean(TPOCS_TOT, na.rm=TRUE),OC_symps_sd=sd(TPOCS_TOT, na.rm=TRUE), Attention=mean(ADHD_I_SUB, na.rm=TRUE), Attention_sd=sd(ADHD_I_SUB, na.rm=TRUE), Hyperactivity=mean(ADHD_HI_SUB, na.rm=TRUE),Hyperactivity_sd=sd(ADHD_HI_SUB, na.rm=TRUE), Restricted_behaviours=mean(RBSALLT, na.rm=TRUE),Restricted_behaviours_sd=sd(RBSALLT, na.rm=TRUE), Social_comm=mean(SCQTOT, na.rm=TRUE),Social_comm_sd=sd(SCQTOT, na.rm=TRUE), ABAS=mean(AB21GCCS, na.rm=TRUE), ABAS_sd=sd(AB21GCCS, na.rm=TRUE))

kable(t(Demographics))
```


##Demographics of clinical diagnoses

```{r, echo=FALSE}
Demographics <- filter(all) %>%
  group_by(clin_diagnosis) %>%
  summarise(N=length(group), Age=mean(age), Age_sd=sd(age), IQ=mean(IQ, na.rm=TRUE), Internalizing=mean(CB68IPTS, na.rm=TRUE),Internalizing_sd=sd(CB68IPTS, na.rm=TRUE), Externalizing=mean(CB68EPTS, na.rm=TRUE), Externalizing_sd=sd(CB68EPTS, na.rm=TRUE), OC_symps=mean(TPOCS_TOT, na.rm=TRUE),OC_symps_sd=sd(TPOCS_TOT, na.rm=TRUE), Attention=mean(ADHD_I_SUB, na.rm=TRUE), Attention_sd=sd(ADHD_I_SUB, na.rm=TRUE), Hyperactivity=mean(ADHD_HI_SUB, na.rm=TRUE),Hyperactivity_sd=sd(ADHD_HI_SUB, na.rm=TRUE), Restricted_behaviours=mean(RBSALLT, na.rm=TRUE),Restricted_behaviours_sd=sd(RBSALLT, na.rm=TRUE), Social_comm=mean(SCQTOT, na.rm=TRUE),Social_comm_sd=sd(SCQTOT, na.rm=TRUE), ABAS=mean(AB21GCCS, na.rm=TRUE), ABAS_sd=sd(AB21GCCS, na.rm=TRUE))

kable(t(Demographics))
```



### Creating statistics table for all SNF features for data-driven groups 
```{r}

Clinical <- filter(all_features) %>%
  group_by(Measure) %>%
  do(tidy(Anova(lm(thickness ~age + GENDER + IQ + group, data=.,), type=2)))

## calculating the Eta sq for each feature
names <- unique(all_features$Measure)
effects <- c("term", "etasq")
for (idx in 1:length(unique(all_features$Measure))){
  print(names[idx])
  stats <- eta_sq(Anova(lm(all[ ,c(names[idx])] ~age + GENDER + IQ + group, data=all)))
  effects <- rbind(effects, stats)
}

effects <- effects[which(effects$term == "group"), ]
effects$Measure <- names
effects <- merge(NMI, effects, by="Measure")
effects <- effects[order(effects$R), ]
effects$etasq <- signif(as.numeric(effects$etasq), digits = 2)

# organizing table with other statistics for each measure
All_results <- Clinical
All_results <- All_results %>% filter(term == "group") 
All_results$p.fdr <- p.adjust(All_results$p.value, method="fdr")

All_results <- All_results %>% arrange(p.value)
All_results$statistic <- signif(All_results$statistic, digits = 3)
All_results$p.value <- signif(All_results$p.value, digits = 3)
All_results$df <- NULL

print(All_results)

top_contributing_clin <- All_results

top_contributing_clin <- merge(NMI, top_contributing_clin, by="Measure")
top_contributing_clin <- top_contributing_clin[order(top_contributing_clin$R), ]

top_contributing_clin$NMI <- signif(top_contributing_clin$NMI, digits = 3)
top_contributing_clin$p.fdr <- signif(top_contributing_clin$p.fdr, digits = 3)

top_contributing_clin$p.fdr <- ifelse(top_contributing_clin$p.fdr > 0.05, "n.s", top_contributing_clin$p.fdr)
top_contributing_clin <- top_contributing_clin[,c("Rank", "Measure", "NMI", "statistic", "p.fdr")]
top_contributing_clin$p.fdr <- format(top_contributing_clin$p.fdr, scientific = TRUE)

top_contributing_clin$Etasq <- effects$etasq
print(top_contributing_clin)

write.csv(top_contributing_clin, file="../../output/2_Comparing_subgroups/all_snf_measures_groupdiffs.csv")

```


### Creating statistics table for all SNF features for for clinical diagnoses - ALL FEATURES
```{r}

Clinical <- filter(all_features) %>%
  group_by(Measure) %>%
  do(tidy(Anova(lm(thickness ~age + GENDER + IQ + clin_diagnosis, data=.,), type=2)))

## calculating the Eta sq for each feature
names <- unique(all_features$Measure)
effects <- c("term", "etasq")
for (idx in 1:length(unique(all_features$Measure))){
  print(names[idx])
  stats <- eta_sq(Anova(lm(all[ ,c(names[idx])] ~age + GENDER + IQ + clin_diagnosis, data=all)))
  effects <- rbind(effects, stats)
}
effects <- effects[which(effects$term == "clin_diagnosis"), ]
effects$Measure <- names
effects <- merge(NMI, effects, by="Measure")
effects <- effects[order(effects$R), ]
effects$etasq <- signif(as.numeric(effects$etasq), digits = 2)

# organizing table with other statistics for each measure
All_results <- Clinical
All_results <- All_results %>% filter(term == "clin_diagnosis") 
All_results$p.fdr <- p.adjust(All_results$p.value, method="fdr")

All_results <- All_results %>% arrange(p.value)
All_results$statistic <- signif(All_results$statistic, digits = 3)
All_results$p.value <- signif(All_results$p.value, digits = 3)
#All_results$p.fdr <- signif(All_results$p.fdr, digits = 3)
#All_results$term <- NULL
All_results$df <- NULL

print(All_results)

top_contributing_clin <- All_results

top_contributing_clin <- merge(NMI, top_contributing_clin, by="Measure")
top_contributing_clin <- top_contributing_clin[order(top_contributing_clin$R), ]

top_contributing_clin$NMI <- signif(top_contributing_clin$NMI, digits = 3)
top_contributing_clin$p.fdr <- signif(top_contributing_clin$p.fdr, digits = 3)

top_contributing_clin$p.fdr <- ifelse(top_contributing_clin$p.fdr > 0.05, "n.s", top_contributing_clin$p.fdr)
top_contributing_clin <- top_contributing_clin[,c("Rank", "Measure", "NMI", "statistic", "p.fdr")]
top_contributing_clin$p.fdr <- format(top_contributing_clin$p.fdr, scientific = TRUE)

top_contributing_clin$Etasq <- effects$etasq

print(top_contributing_clin)

write.csv(top_contributing_clin, file="../../output/2_Comparing_subgroups/all_snf_measures_diagnosticdiffs.csv")


```

### Checking age, sex and IQ interactions

### group by IQ interactions 

```{r}
Clinical <- filter(all_features) %>%
  group_by(Measure) %>%
  do(tidy(Anova(lm(thickness ~age + GENDER + IQ*group, data=.,), type=2)))

## calculating the Eta sq for each feature
names <- unique(all_features$Measure)
effects <- c("term", "etasq")
for (idx in 1:length(unique(all_features$Measure))){
  print(names[idx])
  stats <- eta_sq(Anova(lm(all[ ,c(names[idx])] ~age + GENDER + IQ*group, data=all)))
  effects <- rbind(effects, stats)
}
effects <- effects[which(effects$term == "IQ:group"), ]
effects$Measure <- names
effects <- merge(NMI, effects, by="Measure")
effects <- effects[order(effects$R), ]
effects$etasq <- signif(as.numeric(effects$etasq), digits = 2)

# organizing table with other statistics for each measure
All_results <- Clinical
All_results <- All_results %>% filter(term == "IQ:group") 
All_results$p.fdr <- p.adjust(All_results$p.value, method="fdr")

All_results <- All_results %>% arrange(p.value)
All_results$statistic <- signif(All_results$statistic, digits = 3)
All_results$p.value <- signif(All_results$p.value, digits = 3)
#All_results$p.fdr <- signif(All_results$p.fdr, digits = 3)
#All_results$term <- NULL
#All_results$df <- NULL

print(All_results)

top_contributing_clin <- All_results

top_contributing_clin <- merge(NMI, top_contributing_clin, by="Measure")
top_contributing_clin <- top_contributing_clin[order(top_contributing_clin$R), ]

top_contributing_clin$NMI <- signif(top_contributing_clin$NMI, digits = 3)
top_contributing_clin$p.fdr <- signif(top_contributing_clin$p.fdr, digits = 3)

top_contributing_clin$p.value <- ifelse(top_contributing_clin$p.value > 0.05, "n.s", top_contributing_clin$p.value)
top_contributing_clin <- top_contributing_clin[,c("Rank", "Measure", "NMI", "statistic", "p.value")]
top_contributing_clin$p.fdr <- format(top_contributing_clin$p.fdr, scientific = TRUE)

top_contributing_clin$Etasq <- effects$etasq

print(top_contributing_clin)

write.csv(top_contributing_clin, file="../../output/2_Comparing_subgroups/all_snf_measures_groupbyIQint.csv")

```

### group by sex interactions

```{r}
Clinical <- filter(all_features) %>%
  group_by(Measure) %>%
  do(tidy(Anova(lm(thickness ~age + IQ + GENDER*group, data=.,), type=2)))

## calculating the Eta sq for each feature
names <- unique(all_features$Measure)
effects <- c("term", "etasq")
for (idx in 1:length(unique(all_features$Measure))){
  print(names[idx])
  stats <- eta_sq(Anova(lm(all[ ,c(names[idx])] ~age + IQ + GENDER*group, data=all)))
  effects <- rbind(effects, stats)
}
effects <- effects[which(effects$term == "GENDER:group"), ]
effects$Measure <- names
effects <- merge(NMI, effects, by="Measure")
effects <- effects[order(effects$R), ]
effects$etasq <- signif(as.numeric(effects$etasq), digits = 2)

# organizing table with other statistics for each measure
All_results <- Clinical
All_results <- All_results %>% filter(term == "GENDER:group") 
All_results$p.fdr <- p.adjust(All_results$p.value, method="fdr")

All_results <- All_results %>% arrange(p.value)
All_results$statistic <- signif(All_results$statistic, digits = 3)
All_results$p.value <- signif(All_results$p.value, digits = 3)
#All_results$p.fdr <- signif(All_results$p.fdr, digits = 3)
#All_results$term <- NULL
#All_results$df <- NULL

print(All_results)

top_contributing_clin <- All_results

top_contributing_clin <- merge(NMI, top_contributing_clin, by="Measure")
top_contributing_clin <- top_contributing_clin[order(top_contributing_clin$R), ]

top_contributing_clin$NMI <- signif(top_contributing_clin$NMI, digits = 3)
top_contributing_clin$p.fdr <- signif(top_contributing_clin$p.fdr, digits = 3)

top_contributing_clin$p.value <- ifelse(top_contributing_clin$p.value > 0.05, "n.s", top_contributing_clin$p.value)
top_contributing_clin <- top_contributing_clin[,c("Rank", "Measure", "NMI", "statistic", "p.value")]
top_contributing_clin$p.fdr <- format(top_contributing_clin$p.fdr, scientific = TRUE)

top_contributing_clin$Etasq <- effects$etasq

print(top_contributing_clin)

write.csv(top_contributing_clin, file="../../output/2_Comparing_subgroups/all_snf_measures_groupbysexint.csv")

```


### group by age interactions

```{r}
Clinical <- filter(all_features) %>%
  group_by(Measure) %>%
  do(tidy(Anova(lm(thickness ~ IQ + GENDER + age*group, data=.,), type=2)))

## calculating the Eta sq for each feature
names <- unique(all_features$Measure)
effects <- c("term", "etasq")
for (idx in 1:length(unique(all_features$Measure))){
  print(names[idx])
  stats <- eta_sq(Anova(lm(all[ ,c(names[idx])] ~IQ + GENDER + age*group, data=all)))
  effects <- rbind(effects, stats)
}
effects <- effects[which(effects$term == "age:group"), ]
effects$Measure <- names
effects <- merge(NMI, effects, by="Measure")
effects <- effects[order(effects$R), ]
effects$etasq <- signif(as.numeric(effects$etasq), digits = 2)

# organizing table with other statistics for each measure
All_results <- Clinical
All_results <- All_results %>% filter(term == "age:group") 
All_results$p.fdr <- p.adjust(All_results$p.value, method="fdr")

All_results <- All_results %>% arrange(p.value)
All_results$statistic <- signif(All_results$statistic, digits = 3)
All_results$p.value <- signif(All_results$p.value, digits = 3)
#All_results$p.fdr <- signif(All_results$p.fdr, digits = 3)
#All_results$term <- NULL
#All_results$df <- NULL

print(All_results)

top_contributing_clin <- All_results

top_contributing_clin <- merge(NMI, top_contributing_clin, by="Measure")
top_contributing_clin <- top_contributing_clin[order(top_contributing_clin$R), ]

top_contributing_clin$NMI <- signif(top_contributing_clin$NMI, digits = 3)
top_contributing_clin$p.fdr <- signif(top_contributing_clin$p.fdr, digits = 3)

top_contributing_clin$p.value <- ifelse(top_contributing_clin$p.value > 0.05, "n.s", top_contributing_clin$p.value)
top_contributing_clin <- top_contributing_clin[,c("Rank", "Measure", "NMI", "statistic", "p.value")]
top_contributing_clin$p.fdr <- format(top_contributing_clin$p.fdr, scientific = TRUE)

top_contributing_clin$Etasq <- effects$etasq

print(top_contributing_clin)

write.csv(top_contributing_clin, file="../../output/2_Comparing_subgroups/all_snf_measures_groupbyageint.csv")

```










