---
title: "Creating_cluster_figures"
author: "Grace Jacobs"
output: html_document
---

```{r setup, include=FALSE}
#install.packages("remotes")
#remotes::install_github("LCBC-UiO/ggseg", build_vignettes = FALSE, force = TRUE)

library(ggseg)
library(dplyr)
library(tidyr)
library(haven)
library(ggplot2)
library(ggpubr)
library(plotrix)
library(tidyverse)

source("code/2_Comparing_subgroups/setting_up_data_for_cluster_analysis.r")

all <- read.csv("output/2_Comparing_subgroups/all_snf_measures_groupdiffs.csv")

CT <- read.csv("data/cortical_thickness_ggseg_labels.csv")

CT <- merge(CT, all, by="Measure")

CT$region <- as.character(CT$region)
CT$hemi <- as.character(CT$hemi)
CT$NMI <- round(CT$NMI, digits=3)
CT$Effect_size <- round(CT$Etasq, digits=3)

sub <- read.csv("data/Subcortical_ggseg_labels.csv")
sub <- merge(sub, all, by="Measure")

sub$region <- as.character(sub$region)
sub$hemi <- as.character(sub$hemi)
sub$NMI <- round(sub$NMI, digits=3)
sub$Effect_size <- round(sub$Etasq, digits=3)

```

## Pie chart break down of the 4 clusters by diagnosis

```{r, echo=FALSE}

freq = table(all$clin_diagnosis)
lbls = paste(names(freq), "-", round((freq/176)*100, 1), "%", sep="")

setwd("../../output/2_Comparing_subgroups/Figures/Figure1")
png('pie_all.png')
#pie(freq, main="All participants", labels = lbls, cex=1.5, col=c("darkorange", "deepskyblue1", "aquamarine4"))
pie(freq, main="All participants", labels = lbls, cex=1.5, col=c("black", "darkgray", "white"))
dev.off()

freq = table(clust1$clin_diagnosis)
lbls = paste(names(freq), "-", round((freq/33)*100, 1), "%", sep="")
png('pie_1.png')
pie(freq, main="Cluster 1", labels = lbls,cex=1.5, col=c("black", "darkgray", "white"), lwd= 3)
dev.off()

freq = table(clust2$clin_diagnosis)
lbls = paste(names(freq), "-", round((freq/54)*100, 1), "%", sep="")
png('pie_2.png')
pie(freq, main="Cluster 2", labels = lbls, cex=1.5, col=c("black", "darkgray", "white"))
dev.off()

freq = table(clust3$clin_diagnosis)
lbls = paste(names(freq), "-", round((freq/41)*100, 1), "%", sep="")
png('pie_3.png')
pie(freq, main="Cluster 3", labels = lbls,cex=1.5, col=c("black", "darkgray", "white"))
dev.off()

freq = table(clust4$clin_diagnosis)
lbls = paste(names(freq), "-", round((freq/48)*100, 1), "%", sep="")
png('pie_4.png')
pie(freq, main="Cluster 4", labels = lbls,cex=1.5, col=c("black", "darkgray", "white"))
dev.off()

```

## Visualization of the differences in clinical scores between groups
###NMI scores/contribution

ADHD_I_SUB (Attention)	
ADHD_HI_SUB (Hyperactivity) 
SCQTOT (Social Communication)
CB68EPTOT (Externalizing)	 
CB68IPTOT (Internalizing)	 
TPOCS_TOT (Obsessive Compulsive)	
RBSALLT (Repetative Behaviours)	 

#### Plot of symptom scores by group
```{r, echo=FALSE}
symptoms_stacked$Symptom <- factor(symptoms_stacked$Symptom, labels = c("Hyperactivity", "Inattention", "Externalizing", "Internalizing", "Repetitive\nBehaviours", "Social\nCommunication", "Obsessive\nCompulsive"))

## getting the standard error of each behaviour measure
test <- filter(symptoms_stacked) %>%
  group_by(Symptom, group) %>%
  summarise(std_err=std.error(severity, na.rm=TRUE), sd=sd(severity, na.rm=TRUE),  N=length(group))

symptoms_stacked$std_error <- NA
symptoms_stacked$sd <- NA
for (i in 1:28){
  symp <- (test[i, 1])
  gr <- as.character(test[i, 2])
  symptoms_stacked$std_error <- ifelse(symptoms_stacked$Symptom == symp$Symptom & symptoms_stacked$group == gr, as.numeric(test[i, c("std_err")]), symptoms_stacked$std_error)
  symptoms_stacked$sd <- ifelse(symptoms_stacked$Symptom == symp$Symptom & symptoms_stacked$group == gr, as.numeric(test[i, c("sd")]), symptoms_stacked$sd)
}

ggplot(symptoms_stacked, aes(x=Symptom, y=severity, fill=group)) +
  geom_boxplot() +
  theme_classic() +
  theme(axis.text.x = element_text(size=18, face="bold", angle = 30, hjust = 1), axis.title.x=element_blank(), legend.title=element_text(size=18), axis.text.y=element_text(size=18), axis.title.y=element_text(size=20), legend.text=element_text(size=18)) +
  guides(fill=guide_legend(title="Groups")) +
  scale_fill_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "mediumpurple")) +
  labs(y= "Z-score") +
    stat_summary(fun = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y.., group=group), linetype = "dotted", width = 0.75, position = position_dodge())


ggsave("Group_behaviour_scores_residuals_stderrorbars.png", plot=last_plot(), width = 12, height = 6, units = c("in"), dpi=400, device = "png", path = "../../output/2_Comparing_subgroups/Figures/Figure1/")
```


#### Plot of symptom scores by diagnosis

```{r, echo=FALSE}
symptoms_stacked$Symptom <- factor(symptoms_stacked$Symptom, labels = c("Hyperactivity", "Inattention", "Externalizing", "Internalizing", "Repetitive\nBehaviours", "Social\nCommunication", "Obsessive\nCompulsive"))

test <- filter(symptoms_stacked) %>%
  group_by(Symptom, clin_diagnosis) %>%
  summarise(std_err=std.error(severity, na.rm=TRUE), N=length(clin_diagnosis))

symptoms_stacked$std_error <- NA

for (i in 1:21){
  symp <-(test[i, c("Symptom")])
  gr <- as.character(test[i, 2])
  symptoms_stacked$std_error <- ifelse(symptoms_stacked$Symptom == symp$Symptom & symptoms_stacked$group == gr, as.numeric(test[i, c("std_err")]), symptoms_stacked$std_error)
}


ggplot(symptoms_stacked, aes(x=Symptom, y=severity, fill=clin_diagnosis)) +
  geom_boxplot() +
  theme_classic() +
  theme(axis.text.x = element_text(size=18, face="bold", angle = 30, hjust = 1), axis.title.x=element_blank(), legend.title=element_text(size=18), axis.text.y=element_text(size=18), axis.title.y=element_text(size=20), legend.text=element_text(size=18)) +
  guides(fill=guide_legend(title="Diagnosis")) +
scale_fill_manual(values=c("gray28", "darkgray", "white")) +
  labs(y= "Z-score") +
    stat_summary(fun = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y.., group=clin_diagnosis), linetype = "dotted", width = 0.75, position = position_dodge())

ggsave("Dx_behaviour_scores_residuals_stderrorbars.png", plot=last_plot(), width = 12, height = 6, units = c("in"), dpi=400, device = "png", path ="../../output/2_Comparing_subgroups/Figures/Figure1/")
```

### Follow up Tukey tests to compare groups for each behavioural measure

```{r, echo=FALSE}

### data-driven groups follow up tukey tests
mod <- aov(ADHD_HI_SUB ~ age + IQ + GENDER + group, data=all, na.action=na.exclude)
TukeyHSD(mod, which = "group")
mod <- aov(ADHD_I_SUB ~ age + IQ + GENDER + group, data=all, na.action=na.exclude)
TukeyHSD(mod, which = "group")
mod <- aov(CB68EPTOT ~ age + IQ + GENDER + group, data=all, na.action=na.exclude)
TukeyHSD(mod, which = "group")
mod <- aov(CB68IPTOT ~ age + IQ + GENDER + group, data=all, na.action=na.exclude)
TukeyHSD(mod, which = "group")
mod <- aov(RBSALLT ~ age + IQ + GENDER + group, data=all, na.action=na.exclude)
TukeyHSD(mod, which = "group")
mod <- aov(SCQTOT ~ age + IQ + GENDER + group, data=all, na.action=na.exclude)
TukeyHSD(mod, which = "group")
mod <- aov(TPOCS_TOT ~ age + IQ + GENDER + group, data=all, na.action=na.exclude)
TukeyHSD(mod, which = "group")

### clinical diagnoses follow up tukey tests
mod <- aov(ADHD_HI_SUB ~ age + IQ + GENDER + clin_diagnosis, data=all, na.action=na.exclude)
TukeyHSD(mod, which = "clin_diagnosis")
mod <- aov(ADHD_I_SUB ~ age + IQ + GENDER + clin_diagnosis, data=all, na.action=na.exclude)
TukeyHSD(mod, which = "clin_diagnosis")
mod <- aov(CB68EPTOT ~ age + IQ + GENDER + clin_diagnosis, data=all, na.action=na.exclude)
TukeyHSD(mod, which = "clin_diagnosis")
mod <- aov(CB68IPTOT ~ age + IQ + GENDER + clin_diagnosis, data=all, na.action=na.exclude)
TukeyHSD(mod, which = "clin_diagnosis")
mod <- aov(RBSALLT ~ age + IQ + GENDER + clin_diagnosis, data=all, na.action=na.exclude)
TukeyHSD(mod, which = "clin_diagnosis")
mod <- aov(SCQTOT ~ age + IQ + GENDER + clin_diagnosis, data=all, na.action=na.exclude)
TukeyHSD(mod, which = "clin_diagnosis")
mod <- aov(TPOCS_TOT ~ age + IQ + GENDER + clin_diagnosis, data=all, na.action=na.exclude)
TukeyHSD(mod, which = "clin_diagnosis")

```


### Top contributing features (5) by data type across age for Figure 2

```{r, echo=FALSE}
all$R_parstriangularis_thickavg_resid <- resid(lm(R_parstriangularis_thickavg~GENDER + IQ, data=all, na.action = na.exclude))

ggplot(all, aes(x=age, y=R_parstriangularis_thickavg_resid, color=group)) +
  geom_point() +
  theme_classic() +
  ggtitle("Right Pars Triangularis Thickness") +
      scale_color_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "slateblue")) +
  theme(axis.text.y=element_text(size=20), axis.text.x=element_text(size=20), 
  axis.title.y=element_text(size=22),axis.title.x=element_text(size=22),plot.title = element_text(size=24), legend.title = element_blank(), legend.text =element_text(size=20) ) +
  labs(y= "Cortical Thickness", x="Age (years)") +
  geom_smooth(alpha=0.2, method="lm") +
  scale_y_continuous(limits=c(-0.5, 0.5), breaks =c(-.4, -0.2, 0, 0.2, 0.4, 0.6))
  
ggsave("../../output/2_Comparing_subgroups/Figures/Figure2/parstriangularis_resid_groups.png", plot = last_plot())

```


```{r, echo=FALSE}
all$R_insula_thickavg_resid <- resid(lm(R_insula_thickavg~GENDER + IQ, data=all, na.action = na.exclude))
class(all$age)

ggplot(all, aes(x=age, y=R_insula_thickavg_resid, color=groups)) +
  geom_point() +
  theme_classic() +
  ggtitle("Right Insula Thickness") +
      scale_color_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "slateblue")) +
  theme(axis.text.y=element_text(size=20), axis.text.x=element_text(size=20), 
  axis.title.y=element_text(size=22),axis.title.x=element_text(size=22),plot.title = element_text(size=24), legend.title = element_blank(), legend.text =element_text(size=20) ) +
  labs(y= "Cortical Thickness", x="Age (years)") +
  geom_smooth(alpha=0.2, method="lm") +
  scale_y_continuous(limits=c(-0.5, 0.5), breaks =c(-.4, -0.2, 0, 0.2, 0.4, 0.6))
  
ggsave("../../output/2_Comparing_subgroups/Figures/Figure2/rinsula_resid_groups.png", plot = last_plot())

```


```{r, echo=FALSE}
all$Rpal_resid <- resid(lm(Rpal~GENDER + IQ, data=all, na.action = na.exclude))

ggplot(all, aes(x=age, y=Rpal_resid, color=group)) +
  geom_point() +
  theme_classic() +
  ggtitle("Right Pallidum Volume") +
      scale_color_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "slateblue")) +
  theme(axis.text.y=element_text(size=20), axis.text.x=element_text(size=20), 
  axis.title.y=element_text(size=22),axis.title.x=element_text(size=22),plot.title = element_text(size=24), legend.title = element_blank(), legend.text =element_text(size=20) ) +
  labs(y= "Volume (relative to ICV)", x="Age (years)") +
  geom_smooth(alpha=0.2, method=lm) 
  
ggsave("../../output/2_Comparing_subgroups/Figures/Figure2/rpallidum_resid_groups.png", plot = last_plot())

```

```{r, echo=FALSE}
all$ADHD_I_SUB_resid <- resid(lm(ADHD_I_SUB~GENDER + IQ, data=all, na.action = na.exclude))

ggplot(all, aes(x=age, y=ADHD_I_SUB_resid, color=group)) +
  geom_point() +
  theme_classic() +
  ggtitle("SWAN Inattention Score") +
      scale_color_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "slateblue")) +
  theme(axis.text.y=element_text(size=20), axis.text.x=element_text(size=20), 
  axis.title.y=element_text(size=22),axis.title.x=element_text(size=22),plot.title = element_text(size=24), legend.title = element_blank(), legend.text =element_text(size=20) ) +
  labs(y= "Adjusted Score", x="Age (years)") +
  geom_smooth(alpha=0.2, method="lm") 
  
ggsave("../../output/2_Comparing_subgroups/Figures/Figure2/inattention_resid_groups.png", plot = last_plot())

```

```{r, echo=FALSE}
all$ADHD_HI_SUB_resid <- resid(lm(ADHD_HI_SUB~GENDER + IQ, data=all, na.action = na.exclude))

ggplot(all, aes(x=age, y=ADHD_HI_SUB_resid, color=group)) +
  geom_point() +
  theme_classic() +
  ggtitle("SWAN Hyperactivity Score") +
      scale_color_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "slateblue")) +
  theme(axis.text.y=element_text(size=20), axis.text.x=element_text(size=20), 
  axis.title.y=element_text(size=22),axis.title.x=element_text(size=22),plot.title = element_text(size=24), legend.title = element_blank(), legend.text =element_text(size=20) ) +
  labs(y= "Adjusted Score", x="Age (years)") +
  geom_smooth(alpha=0.2, method="lm") 
  
ggsave("../../output/2_Comparing_subgroups/Figures/Figure2/hyperactivity_resid_groups.png", plot = last_plot())

```


### Group differences across IQ


```{r, echo=FALSE}
all$R_parstriangularis_thickavg_resid <- resid(lm(R_parstriangularis_thickavg~GENDER + age, data=all, na.action = na.exclude))

ggplot(all, aes(x=IQ, y=R_parstriangularis_thickavg_resid, color=group)) +
  geom_point() +
  theme_classic() +
  ggtitle("Right Pars Triangularis Thickness") +
      scale_color_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "slateblue")) +
  theme(axis.text.y=element_text(size=20), axis.text.x=element_text(size=20), 
  axis.title.y=element_text(size=22),axis.title.x=element_text(size=22),plot.title = element_text(size=24), legend.title = element_blank(), legend.text =element_text(size=20) ) +
  labs(y= "Cortical Thickness", x="IQ Score") +
  geom_smooth(alpha=0.2, method="lm") +
  scale_y_continuous(limits=c(-0.5, 0.5), breaks =c(-.4, -0.2, 0, 0.2, 0.4, 0.6))
  
ggsave("../../output/2_Comparing_subgroups/Figures/Figure2/parstriangularis_IQresid_groups.png", plot = last_plot())

```


```{r, echo=FALSE}
all$R_insula_thickavg_resid <- resid(lm(R_insula_thickavg~GENDER + age, data=all, na.action = na.exclude))
class(all$age)

ggplot(all, aes(x=IQ, y=R_insula_thickavg_resid, color=groups)) +
  geom_point() +
  theme_classic() +
  ggtitle("Right Insula Thickness") +
      scale_color_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "slateblue")) +
  theme(axis.text.y=element_text(size=20), axis.text.x=element_text(size=20), 
  axis.title.y=element_text(size=22),axis.title.x=element_text(size=22),plot.title = element_text(size=24), legend.title = element_blank(), legend.text =element_text(size=20) ) +
  labs(y= "Cortical Thickness", x="IQ Score") +
  geom_smooth(alpha=0.2, method="lm") +
  scale_y_continuous(limits=c(-0.5, 0.5), breaks =c(-.4, -0.2, 0, 0.2, 0.4, 0.6))
  
ggsave("../../output/2_Comparing_subgroups/Figures/Figure2/rinsula_IQresid_groups.png", plot = last_plot())

```


```{r, echo=FALSE}
all$Rpal_resid <- resid(lm(Rpal~GENDER + age, data=all, na.action = na.exclude))

ggplot(all, aes(x=IQ, y=Rpal_resid, color=group)) +
  geom_point() +
  theme_classic() +
  ggtitle("Right Pallidum Volume") +
      scale_color_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "slateblue")) +
  theme(axis.text.y=element_text(size=20), axis.text.x=element_text(size=20), 
  axis.title.y=element_text(size=22),axis.title.x=element_text(size=22),plot.title = element_text(size=24), legend.title = element_blank(), legend.text =element_text(size=20) ) +
  labs(y= "Volume (relative to ICV)", x="IQ Score") +
  geom_smooth(alpha=0.2, method=lm) 
  
ggsave("../../output/2_Comparing_subgroups/Figures/Figure2/rpallidum_IQresid_groups.png", plot = last_plot())

```

```{r, echo=FALSE}
all$ADHD_I_SUB_resid <- resid(lm(ADHD_I_SUB~GENDER + age, data=all, na.action = na.exclude))

ggplot(all, aes(x=age, y=ADHD_I_SUB_resid, color=group)) +
  geom_point() +
  theme_classic() +
  ggtitle("SWAN Inattention Score") +
      scale_color_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "slateblue")) +
  theme(axis.text.y=element_text(size=20), axis.text.x=element_text(size=20), 
  axis.title.y=element_text(size=22),axis.title.x=element_text(size=22),plot.title = element_text(size=24), legend.title = element_blank(), legend.text =element_text(size=20) ) +
  labs(y= "Adjusted Score", x="IQ Score") +
  geom_smooth(alpha=0.2, method="lm") 
  
ggsave("../../output/2_Comparing_subgroups/Figures/Figure2/inattention_IQresid_groups.png", plot = last_plot())

```

```{r, echo=FALSE}
all$ADHD_HI_SUB_resid <- resid(lm(ADHD_HI_SUB~GENDER + age, data=all, na.action = na.exclude))


ggplot(all, aes(x=IQ, y=ADHD_HI_SUB_resid, color=group)) +
  geom_point() +
  theme_classic() +
  ggtitle("SWAN Hyperactivity Score") +
      scale_color_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "slateblue")) +
  theme(axis.text.y=element_text(size=20), axis.text.x=element_text(size=20), 
  axis.title.y=element_text(size=22),axis.title.x=element_text(size=22),plot.title = element_text(size=24), legend.title = element_blank(), legend.text =element_text(size=20) ) +
  labs(y= "Adjusted Score", x="IQ Score") +
  geom_smooth(alpha=0.2, method="lm") 
  
ggsave("../../output/2_Comparing_subgroups/Figures/Figure2/hyperactivity_IQresid_groups.png", plot = last_plot())

```

# Supplementary Figures

### Age of groups

```{r, echo=FALSE}
my_comparisons <- list(  c("1", "3"), c("2", "3"), c("4", "3"))

ggplot(all, aes(x=group, y=age, color=group)) +
  geom_boxplot() +
    theme_classic() +
    geom_point(aes(fill = clin_diagnosis, color = group), size = 2, colour= "black", shape = 21, position = position_jitterdodge()) +
   labs(y= "Age (years)", x="Group", legend.title = " Clinical Diagnosis") +
  scale_fill_manual(values=c("black", "darkgray", "white")) +
  scale_color_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "mediumpurple")) +
   theme(axis.text.y=element_text(size=14), axis.text.x=element_text(size=20), 
  axis.title.y=element_text(size=22),axis.title.x=element_blank(), legend.text=element_text(size=16),plot.title = element_text(size=20),legend.title=element_blank()) +
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", method = "t.test", p.adjust.method = "fdr", hide.ns = TRUE)

ggsave("../../output/2_Comparing_subgroups/Figures/Supplement/age_groups.png", plot = last_plot())
```


### Plot of sex distribution across groups and diagnoses

```{r, echo=FALSE}
ggplot(all, aes(x=clin_diagnosis, fill=GENDER)) +
  theme_classic() +
  geom_bar(stat = "Count") +
  labs(y= "Count", x="Group") +
  facet_wrap(~group, nrow = 1)

ggsave("../../output/2_Comparing_subgroups/Figures/Supplement/sex_distribution.png", plot = last_plot(), width = 7, height =3)
```

### IQ across diagnostic groups

```{r, echo=FALSE}
my_comparisons <- list(c("ASD", "OCD"), c("OCD", "ADHD"))

ggplot(all, aes(x=clin_diagnosis, y=IQ)) +
  geom_boxplot() +
    theme_classic() +
  geom_point(aes(fill = group, color = group), size = 2, colour= "black", shape = 21, position = position_jitterdodge()) +
  scale_fill_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "mediumpurple")) +
  ggtitle("General IQ Estimate") +
  labs(y= "IQ Score", x="Group", legend.title = " Clinical Diagnosis") +
    theme(axis.text.y=element_text(size=18), axis.text.x=element_text(size=18), 
  axis.title.y=element_text(size=18),axis.title.x=element_blank(), legend.text=element_text(size=18),plot.title = element_text(size=22), legend.title=element_blank())  +
  stat_compare_means(label = 'p.signif', comparisons = my_comparisons, method = "t.test", p.adjust.method = "fdr", hide.ns = TRUE) 

  
ggsave("../../output/2_Comparing_subgroups/Figures/Supplement/IQ_dx.png", plot = last_plot(), width = 7, height = 5)
```

### IQ across data-driven groups


```{r, echo=FALSE}
my_comparisons <- list(c("1", "2"), c("1", "3"), c("4", "1"))

ggplot(all, aes(x=group, y=IQ, color=group)) +
  geom_boxplot() +
    theme_classic() +
  geom_point(aes(fill = clin_diagnosis, color = group), size = 2, colour= "black", shape = 21, position = position_jitterdodge()) +
    scale_fill_manual(values=c("black", "darkgray", "white")) +
  scale_color_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "mediumpurple")) +
  ggtitle("General IQ Estimate") +
  labs(y= "IQ Score", x="Group", legend.title = " Clinical Diagnosis") +
    theme(axis.text.y=element_text(size=18), axis.text.x=element_text(size=18), 
  axis.title.y=element_text(size=18),axis.title.x=element_text(size=18), legend.text=element_text(size=18),plot.title = element_text(size=22), legend.title=element_blank())  +
  stat_compare_means(label = "p.signif", comparisons = my_comparisons, method = "t.test", p.adjust.method = "none", hide.ns = TRUE) 

ggsave("../../output/2_Comparing_subgroups/Figures/Supplement/IQ_groups.png", plot = last_plot(), width = 7, height = 5)
```



### Check to see what the interaction effect is

```{r, echo=FALSE}

ggplot(all, aes(x=IQ, y=L_middletemporal_thickavg, color=group)) +
  geom_point() +
  theme_classic() +
  ggtitle("Left Middle Temporal Thickness") +
      scale_color_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "slateblue")) +
  theme(axis.text.y=element_text(size=20), axis.text.x=element_text(size=20), 
  axis.title.y=element_text(size=22),axis.title.x=element_text(size=22),plot.title = element_text(size=24), legend.title = element_blank(), legend.text =element_text(size=20) ) +
  labs(y= "Cortical Thickness", x="IQ Score") +
  geom_smooth(alpha=0.2, method="lm") 
  
ggsave("../../output/2_Comparing_subgroups/Figures/Supplement/L_middletemporal_thickavg_IQ_int_groups.png", plot = last_plot())

```

```{r, echo=FALSE}

ggplot(all, aes(x=IQ, y=L_parsorbitalis_thickavg, color=group)) +
  geom_point() +
  theme_classic() +
  ggtitle("Left Pars Orbitalis Thickness") +
      scale_color_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "slateblue")) +
  theme(axis.text.y=element_text(size=20), axis.text.x=element_text(size=20), 
  axis.title.y=element_text(size=22),axis.title.x=element_text(size=22),plot.title = element_text(size=24), legend.title = element_blank(), legend.text =element_text(size=20) ) +
  labs(y= "Cortical Thickness", x="IQ Score") +
  geom_smooth(alpha=0.2, method="lm") 
  
ggsave("../../output/2_Comparing_subgroups/Figures/Supplement/L_parsorbitalis_thickavg_IQ_int_groups.png", plot = last_plot())

```

## Looking at social communication scores and obsessive-compulsive scores for the ASD subgroup in Group 1 compared to ASD participants in other groups


```{r, echo=FALSE}
test <- all[which(all$clin_diagnosis == "ASD"), ]
my_comparisons <- list(c("1", "2"), c("1", "3"))

ggplot(test, aes(x=group, y=TPOCS_TOT, color=group)) +
  geom_boxplot() +
    theme_classic() +
  geom_point(aes(fill = clin_diagnosis, color = group), size = 2, colour= "black", shape = 21, position = position_jitterdodge()) +
    scale_fill_manual(values=c("darkgray")) +
  scale_color_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "mediumpurple")) +
  ggtitle("Obsessive-Compulsive Score") +
  labs(y= "TOCS Score", x="Group", legend.title = " Clinical Diagnosis") +
    theme(axis.text.y=element_text(size=18), axis.text.x=element_text(size=18), 
  axis.title.y=element_text(size=18),axis.title.x=element_text(size=18), legend.text=element_text(size=18),plot.title = element_text(size=22), legend.title=element_blank())  +
  stat_compare_means(label = "p.signif", comparisons = my_comparisons, method = "t.test", p.adjust.method = "fdr", hide.ns = TRUE) 

ggsave("../../output/2_Comparing_subgroups/Figures/Supplement/ASD_OCDsubgroup.png", plot = last_plot(), width = 7, height = 5)
```

```{r, echo=FALSE}
test <- all[which(all$clin_diagnosis == "ASD"), ]
my_comparisons <- list(c("1", "2"), c("1", "3"), c("4", "1"))

ggplot(test, aes(x=group, y=SCQTOT, color=group)) +
  geom_boxplot() +
    theme_classic() +
  geom_point(aes(fill = clin_diagnosis, color = group), size = 2, colour= "black", shape = 21, position = position_jitterdodge()) +
    scale_fill_manual(values=c("darkgray")) +
  scale_color_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "mediumpurple")) +
  ggtitle("Social Communication Score") +
  labs(y= "SCQ Score", x="Group", legend.title = " Clinical Diagnosis") +
    theme(axis.text.y=element_text(size=18), axis.text.x=element_text(size=18), 
  axis.title.y=element_text(size=18),axis.title.x=element_text(size=18), legend.text=element_text(size=18),plot.title = element_text(size=22), legend.title=element_blank())  +
  stat_compare_means(label = "p.signif", comparisons = my_comparisons, method = "t.test", p.adjust.method = "fdr", hide.ns = TRUE) 

ggsave("../../output/2_Comparing_subgroups/Figures/Supplement/Social_comm_ASDsubgroup.png", plot = last_plot(), width = 7, height = 5)
```

```{r, echo=FALSE}
test <- all[which(all$clin_diagnosis == "OCD"), ]
my_comparisons <- list(c("1", "2"), c("1", "3"))

ggplot(test, aes(x=group, y=TPOCS_TOT, color=group)) +
  geom_boxplot() +
    theme_classic() +
  geom_point(aes(fill = clin_diagnosis, color = group), size = 2, colour= "black", shape = 21, position = position_jitterdodge()) +
    scale_fill_manual(values=c("white")) +
  scale_color_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "mediumpurple")) +
  ggtitle("Obsessive-Compulsive Score") +
  labs(y= "TOCS Score", x="Group", legend.title = " Clinical Diagnosis") +
    theme(axis.text.y=element_text(size=18), axis.text.x=element_text(size=18), 
  axis.title.y=element_text(size=18),axis.title.x=element_text(size=18), legend.text=element_text(size=18),plot.title = element_text(size=22), legend.title=element_blank())  +
  stat_compare_means(label = "p.signif", method = "t.test", p.adjust.method = "fdr", hide.ns = TRUE) 

ggsave("../../output/2_Comparing_subgroups/Figures/Supplement/OCD_OCDsubgroup.png", plot = last_plot(), width = 7, height = 5)
```


```{r, echo=FALSE}
test <- all[which(all$clin_diagnosis == "OCD"), ]

ggplot(test, aes(x=group, y=SCQTOT, color=group)) +
  geom_boxplot() +
    theme_classic() +
  geom_point(aes(fill = clin_diagnosis, color = group), size = 2, colour= "black", shape = 21, position = position_jitterdodge()) +
    scale_fill_manual(values=c("white")) +
  scale_color_manual(values=c("palevioletred", "darkkhaki", "turquoise3", "mediumpurple")) +
  ggtitle("Social Communication Score") +
  labs(y= "SCQ Score", x="Group", legend.title = " Clinical Diagnosis") +
    theme(axis.text.y=element_text(size=18), axis.text.x=element_text(size=18), 
  axis.title.y=element_text(size=18),axis.title.x=element_text(size=18), legend.text=element_text(size=18),plot.title = element_text(size=22), legend.title=element_blank())  +
  stat_compare_means(label = "p.signif", method = "t.test", p.adjust.method = "fdr", hide.ns = TRUE) 

ggsave("../../output/2_Comparing_subgroups/Figures/Supplement/Social_comm_OCDsubgroup.png", plot = last_plot(), width = 7, height = 5)
```

## Cortical Thickness effect size spatial map
```{r}
#ggseg(atlas=dkt, position="stacked", mapping=aes(fill=area), show.legend = F)

results = data.frame(cbind(area=CT$region, p=CT$Effect_size, hemi=CT$hemi), stringsAsFactors=F)

results %>% 
  ggseg(mapping=aes(fill=as.numeric(p)), position="stacked", colour="white") +
  scale_fill_gradientn(colours = c("darkred","darkorange2","gold"),na.value="grey", breaks=c(0,0.1,0.2, 0.3, 0.4),labels=c(0,0.1,0.2, 0.3, 0.4), limits=c(0,0.4))

ggsave("../../output/2_Comparing_subgroups/Figures/Supplement/CT_effectsize.png", plot = last_plot())
```


## Subcortical volume effect sizes spatial map

```{r}
results <- data.frame(cbind(area=as.character(sub$region), p=sub$Effect_size, hemi=as.character(sub$hemi)))
results$p <- as.numeric(as.character(results$p))

results %>% 
  ggseg(atlas=aseg, mapping=aes(fill=p)) +
  scale_fill_gradientn(colours = c("darkred","darkorange2","gold"),na.value="grey", breaks=c(0,0.1,0.2, 0.3, 0.4),labels=c(0,0.1,0.2, 0.3, 0.4), limits=c(0,0.4))


ggsave("../../output/2_Comparing_subgroups/Figures/Supplement/subcortical_effectsize.png", plot = last_plot()) 

```
