
# Visualizing model stability output from the bootstrapping script

```{r, echo=FALSE}
library(corrplot)
library(dplyr)
library(tidyr)
library(ggplot2)
library(reshape)
library(extrafont)

insertRow <- function(existingDF, newrow, r) {
  existingDF[seq(r+1,nrow(existingDF)+1),] <- existingDF[seq(r,nrow(existingDF)),]
  existingDF[r,] <- newrow
  existingDF
}

# Loading  csvs of each data type (no headers)
directory <- ("../../output/3_Stability/")
# number of participants
num_subs <- 176
# percent agreement matrix
percent_agree_5 <-  read.csv(file.path(directory, paste("Percent_agree_4c_1000perms.csv", sep="")))
percent_agree_5$X <- NULL
# adjusted rand index and rand index
nonrandindex <- read.csv(file.path(directory, paste("Rand_indices_4c_1000perms.csv", sep="")))
nonrandindex$X <- NULL
randindex <- nonrandindex[ ,1:1000]
# pulling out specifically the adjusted rand index values
adjrandindex <- nonrandindex[ ,1001:2000]

# NMI scores
actual_names <- read.csv("../../data/NMI_names.csv")
measures <- read.csv("../../data/measure_names.csv")
top_contributing <- read.csv("../../output/1_SNF_analysis/all_scores_k18_0.8_1000perms.csv")
names(top_contributing)[names(top_contributing) == "Measure"] <- "Measures"

NMI <- read.csv(file=file.path(directory, paste("NMI_scores_0.8_1000perms.csv", sep="")))
NMI$X <- NULL

data <- cbind(measures, NMI)
data$Average <- rowSums(data[,2:1001])/1000

# final SNF clusters
clusters <- read.csv("../../output/1_SNF_analysis/4clust_groups_k18_0.8_1000perms.csv")
# reordering clusters from high to low symptom/functioning for better interpretability throughout results
clusters$groups_2 <- ifelse(clusters$groups == "1", "2", NA)
clusters$groups_2 <- ifelse(clusters$groups == "2", "4", clusters$groups_2)
clusters$groups_2 <- ifelse(clusters$groups == "3", "3", clusters$groups_2)
clusters$groups_2 <- ifelse(clusters$groups == "4", "1", clusters$groups_2)
clusters$groups <- clusters$groups_2

# renaming percent agreement and adding cluster column
clusts <- clusters$groups
pa <- percent_agree_5
pa$groups <- clusters$groups

## makes groups the first column
pa <- pa[ ,c((num_subs+1), 1:num_subs)]
clusts <- c(0, clusts)
pa <- insertRow(pa, clusts, 1)
## now have groups along side and along top
```


## Participant agreement matrices

```{r, echo=FALSE}
### getting percentage agreement matrix for Group 1
group1 <- pa[which(pa$groups == "1" | pa$groups == "0"), which(pa[1,] == "1" | pa[1,] == "0")]
group1 <- group1[-1, -1]
## checking class
sapply(group1, class)
# making numeric
group1 <- as.data.frame(sapply(group1, as.numeric))
png(file.path(directory, paste("Group1_PercentAgree_clusters.png", sep="")))
corrplot(as.matrix(group1),cl.lim = c(0, 1), method="color", order="hclust")
dev.off()

# getting group averages
subs=seq(1,length(group1))
group1_avgs = data.frame("ID"=subs,"avg_percent"=numeric(length(subs)))
for (sub in subs){
  group1_avgs[subs, 2] <- rowSums(group1[subs,] )/(num_subs - rowSums(group1[subs,]== 0))
}


### getting percentage agreement matrix for Group 2
group2 <- pa[which(pa$groups == "2" | pa$groups == "0"), which(pa[1,] == "2" | pa[1,] == "0")]
group2 <- group2[-1, -1]
## checking class
sapply(group2, class)
# making numeric
group2 <- as.data.frame(sapply(group2, as.numeric))
png(file.path(directory, paste("Group2_PercentAgree_clusters.png", sep="")))
corrplot(as.matrix(group2),cl.lim = c(0, 1), method="color", order="hclust")
dev.off()
subs=seq(1,length(group2))
group2_avgs = data.frame("ID"=subs,"avg_percent"=numeric(length(subs)))
for (sub in subs){
  group2_avgs[subs, 2] <- rowSums(group2[subs,] )/(num_subs - rowSums(group2[subs,]== 0))
}


### getting percentage agreement matrix for Group 3
group3 <- pa[which(pa$groups == "3" | pa$groups == "0"), which(pa[1,] == "3" | pa[1,] == "0")]
group3 <- group3[-1, -1]
group3 <- as.data.frame(sapply(group3, as.numeric))

png(file.path(directory, paste("Group3_PercentAgree_clusters.png", sep="")))
corrplot(as.matrix(group3),cl.lim = c(0, 1), method="color", order="hclust")
dev.off()
subs=seq(1,length(group3))
group3_avgs = data.frame("ID"=subs,"avg_percent"=numeric(length(subs)))
for (sub in subs){
  group3_avgs[subs, 2] <- rowSums(group3[subs,] )/(179 - rowSums(group3[subs,]== 0))
}


### getting percentage agreement matrix for Group 4
group4 <- pa[which(pa$groups == "4" | pa$groups == "0"), which(pa[1,] == "4" | pa[1,] == "0")]
group4 <- group4[-1, -1]
group4 <- as.data.frame(sapply(group4, as.numeric))

png(file.path(directory, paste("Group4_PercentAgree_4clusters.png", sep="")))
corrplot(as.matrix(group4),cl.lim = c(0, 1), method="color", order="hclust")
dev.off()
subs=seq(1,length(group4))
group4_avgs = data.frame("ID"=subs,"avg_percent"=numeric(length(subs)))
for (sub in subs){
  group4_avgs[subs, 2] <- rowSums(group4[subs,] )/(179 - rowSums(group4[subs,]== 0))
}


### getting percentage agreement matrix for all groups
all <- pa
all[1, ] <- all[, 1]
all <- pa[order(pa$group),order(pa[1, ])]
all <- all[-1, -1]
all <- as.data.frame(sapply(all, as.numeric))

png(file.path(directory, paste("all_PercentAgree_4clusters.png", sep="")))
corrplot(as.matrix(all),cl.lim = c(0, 1), method="color")
dev.off()

subs=seq(1,length(all))
all_avgs = data.frame("ID"=subs,"avg_percent"=numeric(length(subs)))
for (sub in subs){
  all_avgs[subs, 2] <- rowSums(all[subs,] )/(185 - rowSums(all[subs,]== 0))
}

```

## Getting the mean participant agreement within and across groups

```{r, echo=FALSE}
## mean for each group
no_nums <- all

# within group 1
one <- no_nums[1:33, 1:33]
one <- as.data.frame(sapply(one, as.numeric))

subs=seq(1,length(one)) #number of subjects
one_avgs = data.frame("ID"=subs,"avg_percent"=numeric(length(subs)))
for (sub in subs){
  one_avgs[subs, 2] <- (rowSums(one[subs,]) - 1)/(length(one) - 1)
}

first_group_mean <- mean(one_avgs$avg_percent)

# group 1 and 2
one <- no_nums[1:33, 34:87]
one <- as.data.frame(sapply(one, as.numeric))

subs=seq(1,length(one))
one_avgs = data.frame("ID"=subs,"avg_percent"=numeric(length(subs)))
for (sub in subs){
  one_avgs[subs, 2] <- (rowSums(one[subs,]) - 1)/(length(one) - 1)
}
one_avgs <- na.omit(one_avgs)
first_second <- mean(one_avgs$avg_percent)

# group 1 and group 3
one <- no_nums[1:33, 88:128]
one <- as.data.frame(sapply(one, as.numeric))
subs=seq(1,length(one))
one_avgs = data.frame("ID"=subs,"avg_percent"=numeric(length(subs)))
for (sub in subs){
  one_avgs[subs, 2] <- (rowSums(one[subs,]) - 1)/(length(one) - 1)
}
one_avgs <- na.omit(one_avgs)
first_third <- mean(one_avgs$avg_percent)

# group 1 and group 4
one <- no_nums[1:33, 129:176]
one <- as.data.frame(sapply(one, as.numeric))
subs=seq(1,length(one))
one_avgs = data.frame("ID"=subs,"avg_percent"=numeric(length(subs)))
for (sub in subs){
  one_avgs[subs, 2] <- (rowSums(one[subs,]) - 1)/(length(one) - 1)
}
one_avgs <- na.omit(one_avgs)
first_fourth <- mean(one_avgs$avg_percent)

# withing group 2
no_nums <- all
one <- no_nums[34:87, 34:87]
one <- as.data.frame(sapply(one, as.numeric))

subs=seq(1,length(one))
one_avgs = data.frame("ID"=subs,"avg_percent"=numeric(length(subs)))
for (sub in subs){
  one_avgs[subs, 2] <- (rowSums(one[subs,]) - 1)/(length(one) - 1)
}
second <- mean(one_avgs$avg_percent)

# group 2 and group 3
one <- no_nums[88:128, 34:87]
one <- as.data.frame(sapply(one, as.numeric))

subs=seq(1,length(one))
one_avgs = data.frame("ID"=subs,"avg_percent"=numeric(length(subs)))
for (sub in subs){
  one_avgs[subs, 2] <- (rowSums(one[subs,]) - 1)/(length(one) - 1)
}
one_avgs <- na.omit(one_avgs)
second_third <- mean(one_avgs$avg_percent)

# group 2 and group 4
one <- no_nums[129:176, 34:87]
one <- as.data.frame(sapply(one, as.numeric))

subs=seq(1,length(one))
one_avgs = data.frame("ID"=subs,"avg_percent"=numeric(length(subs)))
for (sub in subs){
  one_avgs[subs, 2] <- (rowSums(one[subs,]) - 1)/(length(one) - 1)
}
one_avgs <- na.omit(one_avgs)
second_fourth <- mean(one_avgs$avg_percent)

# group 3 and group 4
one <- no_nums[129:176, 88:128]
one <- as.data.frame(sapply(one, as.numeric))

subs=seq(1,length(one))
one_avgs = data.frame("ID"=subs,"avg_percent"=numeric(length(subs)))
for (sub in subs){
  one_avgs[subs, 2] <- (rowSums(one[subs,]) - 1)/(length(one) - 1)
}
one_avgs <- na.omit(one_avgs)
third_fourth <- mean(one_avgs$avg_percent)

# within group 3
one <- no_nums[88:128, 88:128]
one <- as.data.frame(sapply(one, as.numeric))

subs=seq(1,length(one))
one_avgs = data.frame("ID"=subs,"avg_percent"=numeric(length(subs)))
for (sub in subs){
  one_avgs[subs, 2] <- (rowSums(one[subs,]) - 1)/(length(one) - 1)
}
one_avgs <- na.omit(one_avgs)
third <- mean(one_avgs$avg_percent)

# within group 4
one <- no_nums[129:176, 129:176]
one <- as.data.frame(sapply(one, as.numeric))

subs=seq(1,length(one))
one_avgs = data.frame("ID"=subs,"avg_percent"=numeric(length(subs)))
for (sub in subs){
  one_avgs[subs, 2] <- (rowSums(one[subs,]) - 1)/(length(one) - 1)
}
one_avgs <- na.omit(one_avgs)
fourth <- mean(one_avgs$avg_percent)
```

## Calculating the average adjusted rand index for the 4 clusters

```{r, echo=FALSE}
## getting the average adj list rand for 4 clusters
list_randindex_4 <- randindex
list_randindex_4$Column <- seq(1:length(list_randindex_4[,1]))
index <- melt(list_randindex_4, id.vars=c('Column'),var='Index')
index <- na.omit(index)
index$cluster_num <- "4 Clusters"
mean(index$value) # 0.80

adjrandindex <- adjrandindex
adjrandindex$Column <- seq(1:length(adjrandindex[,1]))
adjrandindex <- melt(adjrandindex, id.vars=c('Column'),var='Index')
adjrandindex <- na.omit(adjrandindex)
adjrandindex$cluster_num <- "4 Clusters"
mean(adjrandindex$value) # 0.46

```

## Plotting the number of times that a feature was in the top 35 features based on NMI

```{r, echo=FALSE}
top_NMI_measures <- data.frame(matrix(0, nrow = 35, ncol = 1000))

# narrowing down order of features to the top 35 from the NMI file
i=1
for (i in seq(1:length(NMI))) {
  intermediate <- NMI[ , i]
  intermediate <- cbind(measures, intermediate)
  intermediate$intermediate <- as.numeric(as.character(intermediate$intermediate))
  intermediate <- intermediate[order(-intermediate$intermediate), ]

  top_NMI_measures[ ,i] <- intermediate[1:35, 1]
}

top_measures <- top_NMI_measures
top_measures$Column <- seq(1:length(top_measures[,1]))
top_measures <- melt(top_measures, id.vars=c('Column'),var='Index')
top_measures$Column <- NULL
top_measures$Index <- NULL

# One variable short - because it was in the top 35 zero times
measure_count <- as.data.frame(table(top_measures$value))
names(measure_count)[names(measure_count) == "Var1"] <- "Measures"
measure_count <- measure_count[order(measure_count$Freq),]

## adjusting the variables to look better in the plot
ranking <- merge(measure_count, top_contributing, by="Measures", all.y = TRUE)
ranking$colour <- ifelse(ranking$Rank < 36, "Top 35", "Other")
ranking$colour = factor(ranking$colour, levels=c("Top 35", "Other"))

# turning the freuquency into a percentage
ranking$Freq <- ranking$Freq/10
class(ranking$Rank)

#now can also rbind actual names
actual_names$NMI <- NULL
ranking <- merge(actual_names, ranking, by="Rank")

```

### Showing all features - % of time in top 35 features across permutations

```{r, echo=FALSE}
names <- ranking$Name

ggplot(data=ranking, aes(x=Rank, y=Freq, fill=Freq)) +
  theme_classic() +
  geom_bar(stat="identity") + 
  coord_flip() +
  scale_fill_gradient2(low='lightgray', mid='yellow', high='#FC4E07', limits=c(0, 100), name="Percentage", guide =guide_colourbar(barwidth = 3, barheight = 10)) +
scale_x_reverse(breaks=seq(1,135,1), labels=names, sec.axis = sec_axis(~.*1, breaks=seq(1,135,1))) +  scale_y_continuous(n.breaks = 10) +
  labs(y="Percentage of Time As Top 35 Feature", x="Feature Name In Order of Rank") +
  theme(axis.text.y=element_text(size=12), axis.text.x=element_text(size=18), 
  axis.title.y=element_text(size=24),axis.title.x=element_text(size=24), legend.text=element_text(size=24), legend.title=element_text(size=24),plot.title = element_text(size=22)) +
  facet_grid(colour ~ ., scales = "free", space="free") +
  theme(strip.text.y = element_text(size = 18))
  #xlim(135, 1)

ggsave(file=file.path(directory, paste("NMI_top_ranking_frequency.png")), plot = last_plot(), width=13, height=20)
```


## Showing only 35 top contributing features for Figure 2

```{r, echo=FALSE}
subset <- ranking[which(ranking$Rank < 36), ]
names <- subset$Name

ggplot(data=subset, aes(x=Rank, y=Freq, fill=Freq)) +
  theme_classic() +
  geom_bar(stat="identity") + 
  coord_flip() +
  scale_fill_gradient2(low='lightgray', mid='yellow', high='#FC4E07', space='Lab', breaks=seq(0,100,25)) +
  scale_x_reverse(breaks=seq(1,35,1), labels=names, sec.axis = sec_axis(~.*1, breaks=seq(1,35,1), name = "Feature Rank")) +
  scale_y_continuous(breaks=seq(0,100,10)) +
  labs(y="Percentage of Time As Top 35 Feature") +
  theme(axis.text.y=element_text(size=14), axis.text.x=element_text(size=20), 
  axis.title.y=element_text(size=24),axis.title.x=element_text(size=24), legend.text=element_text(size=18),plot.title = element_text(size=22))
  #xlim(135, 1)

ggsave(file=file.path(directory, paste("Top_35_ranking_frequency.png", sep="")), plot = last_plot(), width=15, height=8)
```




